---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)
```

# gamblr

<!-- badges: start -->
[![GitHub issues](https://img.shields.io/github/issues/gtwa-bio/gamblr)](https://github.com/gtwa-bio/gamblr/issues)
[![GitHub pulls](https://img.shields.io/github/issues-pr/gtwa-bio/gamblr)](https://github.com/gtwa-bio/gamblr/pulls)
<!-- badges: end -->

The goal of `gamblr` is to provide toy gambling functions to play with in R. It's nothing special, but I hope you can have fun with it!

## Installation instructions
Currently, there are no plans to submit this package to CRAN or BioConductor.

Get the development version from [GitHub](https://github.com/gtwa-bio/gamblr) with:

```{r 'install_dev', eval = FALSE}
BiocManager::install("gtwa-bio/gamblr")
```


## Example

This is a basic example which shows you how to solve a common problem:

```{r example, eval = requireNamespace('gamblr')}
library("gamblr")

## die gambling game
die_gamble(20, "same")
#> Die 1 is: 2.
#> Die 2 is: 4.
#> [1] "You lost! -$20"
#> [1] "Your bank is now: $80"

## coing gambling game
coin_gamble(20, "heads")
#> [1] "The coin flip is: tails"
#> [1] "You lost! -$20"
#> [1] "Your bank is now: $80"
```


## Citation

Below is the citation output from using `citation('gamblr')` in R. Please
run this yourself to check for any updates on how to cite __gamblr__.

```{r 'citation', eval = requireNamespace('gamblr')}
print(citation('gamblr'), bibtex = TRUE)
```

Please note that the `gamblr` was only made possible thanks to many other R and bioinformatics software authors, which are cited either in the vignettes and/or the paper(s) describing this package.

## Code of Conduct

Please note that the `gamblr` project is released with a [Contributor Code of Conduct](http://bioconductor.org/about/code-of-conduct/). By contributing to this project, you agree to abide by its terms.

## Development tools

* Continuous code testing is possible thanks to [GitHub actions](https://www.tidyverse.org/blog/2020/04/usethis-1-6-0/)  through `r BiocStyle::CRANpkg('usethis')`, `r BiocStyle::CRANpkg('remotes')`, and `r BiocStyle::CRANpkg('rcmdcheck')` customized to use [Bioconductor's docker containers](https://www.bioconductor.org/help/docker/) and `r BiocStyle::Biocpkg('BiocCheck')`.
* Code coverage assessment is possible thanks to [codecov](https://codecov.io/gh) and `r BiocStyle::CRANpkg('covr')`.
* The [documentation website](http://gtwa-bio.github.io/gamblr) is automatically updated thanks to `r BiocStyle::CRANpkg('pkgdown')`.
* The code is styled automatically thanks to `r BiocStyle::CRANpkg('styler')`.
* The documentation is formatted thanks to `r BiocStyle::CRANpkg('devtools')` and `r BiocStyle::CRANpkg('roxygen2')`.

For more details, check the `dev` directory.

This package was developed using `r BiocStyle::Biocpkg('biocthis')`.


